My Bash Notes

### 2019-07-22 Ubuntu_setup/mylinux.Rmd
update

---
title: "My Bash Notes"
subtitle: "A Quick Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

```{bash, preprocess-dir, include=FALSE}
cd ~/bash_pract && rm -r dir
mkdir dir dir/dir2
touch dir/{01..03}-file.txt dir/README
```

>>>>

---
title: "My Bash Notes"
subtitle: "A Quick Reference"
author: "Yongfu Liao"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
link-citations: yes
output:
  rmdformats::readthedown:
    use_bookdown: true
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

```{bash, preprocess-dir, include=FALSE}
[[ -d ~/bash_pract ]] || mkdir ~/bash_pract
cd ~/bash_pract && rm -r dir
mkdir dir dir/dir2
touch dir/{01..03}-file.txt dir/README
```
